Comparison of Analytical and Artificial Neural Network models in predicting hot deformation behavior of AISI P20

### 2022-11-18 Article.tex
Final modification before sharing

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
%\newcommand{\e}[1]{\exp\left({#1}\right)}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
\DeclareRobustCommand{\versus}{\emph{vs.}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
%\DeclareMathOperator{\ANN2}{sig}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
%\DeclareMathOperator{\sech}{sech}
%\DeclareMathOperator{\ANN2}{sig}

\usepackage{esvect}
% Redefine the esvector shape to remove overlapping
\def\traitfill@#1#2#3#4{%
  $\m@th\mkern2mu\relax#4#1\mkern-1.5mu %on met \relbaredd au d\'ebut
   \cleaders\hbox{$#4\mkern-0.3mu#2\mkern-0.3mu$}\hfill %remplit avec relbareda
   \mkern-1.5mu#3$%
}
\renewcommand{\overrightarrow}{\vv}

% This is used to add comments into the text
\usepackage{soul} %Can also be used to highlight text with \hl{highlighted text}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:} #1}}\endgroup} }

@@

\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation-extrapolation capacity validation}

\author[LGP]{Pierre Tize Mha}
\author[ETS]{Prashant Dhondapure}
\author[LGP]{Amèvi Tongne}
\author[ETS]{Mohammad Jahazi}
\author[LGP]{Olivier Pantalé \corref{cor1}}
\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}

\begin{abstract}
An analysis of the use of analytical models and Artificial Neural Networks (ANN) is proposed in this paper to study the high-temperature deformation behavior of AISI P20 alloy during hot compression tests, on a Gleeble thermomechanical simulator, over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$). 
From the experimental data (stress-strain curves), 5 analytical models such as Johnson-Cook (JC), Modified Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arrhenius (AR) and PTM on the one hand, and an ANN model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow of this alloy. 
The comparison between the analytical models, the ANN model and the experimental results, carried out on the basis of the Mean Absolute Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$), allowed us to qualify the fidelity of these models.
We were able to show that the JC and MZA models are not suitable to predict the high temperature behavior of the AISI P20 alloy, while the HS, PTM and AR models can be used to predict the behavior of this alloy with an acceptable error. 
On the other hand, the ANN model results show excellent agreement between the predicted flow stresses $\sigma^y$ and experiment with very low error.
To validate the performance of these models, their ability to interpolate and extrapolate the experimental data was also tested. 
The HS, PTM and AR analytical models have shown a good interpolation and extrapolation capacity with a notable superiority for the AR model compared to the other two. 
The ANN model is still superior to the AR model from the point of view of its global behavior and its performance.
\end{abstract}

@@

%--------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%--------------------------------------------------------------------------
Continuous casting and rolling techniques are an integral part of material forming methods.
Advantages of this method include increased process efficiency, energy savings, improved casting quality and easier mechanization and automation.
Deformation, a complex process involving simultaneous elastic and plastic deformation, is accompanied by high temperatures, high strain rates, and complex and variable frictional conditions \cite{He-2013}, for which, analytical methods are not available for quantitative study and analysis of the deformation mechanism.
On the other hand, conducting experimental tests is not only time-consuming but also requires a high financial investment \cite{Changizian-2012}.
As an alternative approach to the previous two, the Finite Element Method (FEM) is widely used as a tool for analysis and optimization of process parameters in the processing of various materials.
Finite element modeling effectively compensates for the shortcomings of analytical and experimental methods and is playing an increasingly important role in determining process parameters, improving product quality, and gaining in-depth knowledge of deformation mechanisms.
For example, FEM has been widely used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Qin-2010, Mandal-2009, Ji-2018}.

Hot forming processes are an essential step in the manufacture of mechanical components and directly affect the final quality of the products through their strong influence on the micro-structure and mechanical properties \cite{Ashtiani-2012}.
Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and re-crystallization), which very often occur during hot working, influence the behavior and deformation of materials.
The complexity of the thermomechanical behavior usually leads to the fact that it can only be taken into account accurately by using a numerical approach to obtain the response of the material under the specified loading conditions.
To this end, a mathematical formulation is typically used to represent the flow of a material in a form that can be used in finite element software \cite{Lin-2008-P, Wu-2012}.

For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models.
Thus, various forms of constitutive equations have been proposed to describe the flow of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Lin-2011, Shin-2010, Rusinek-2010, Pantale-2021}.
Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes.
The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{Khan-2004, NematNasser-2003}.
However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior.
We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}.
To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}.
Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
However, this model has other drawbacks related to the limit value of the test temperature.
Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}.
Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.

The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the deformation energy of the material \cite{Jonas-1969, Zhang-2012, Mostafaei-2012}.
Its original formulation has been revised several times to correctly describe the resulting experimental behavior.
In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors.
For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that his model could predict the high-temperature flow of a magnesium alloy.
Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.

Users of the Forge software make extensive use of the model developed by Hansel and Spittel \cite{Hensel-1978}, commonly referred to as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on the three physical variables.
Unlike the JC model, this formulation is based on parameters that are determined simultaneously.
This model is simple to use and has 8 parameters that are easy to determine.
The limitation of this model is its loss of accuracy in some cases when the 8 parameters are defined.
This is why many works often limit its identification to only 5, 6 or 7 parameters.
This has been verified in our study where the smallest error of the model is obtained with only 7 parameters identified.

@@

Behavior modeling based on an artificial neural network is an approach to predict the flow of materials without requiring a mathematical formulation of the flow law.
It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress by an analytical model whose parameters are identified by a classical regression method is limited.
Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
Consequently, ANNs have been successfully applied to predict the flow of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}.
They provide a fundamentally different approach to statistical or numerical techniques for modeling materials.

In this work, the high-temperature thermomechanical behavior of AISI P20 modified carbon steel subjected to compression tests in a Gleeble thermomechanical simulator was studied.
From the experimental data obtained from the compression tests, five analytical models were identified in order to select the one that best describes the behavior of this alloy.
A flow model based on an artificial neural network was also developed and identified, and a comparative study between the five analytical models and the ANN model is proposed.
A fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.

The main parts of this work are as follows: Section \ref{sec:Materials} presents the hardware (Gleeble thermomechanical simulator), the experimental procedure, the material and the results of the compression tests performed for this study.
Section \ref{sec:ConstLaws} is devoted to the presentation of the five analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models.
Section \ref{sec:IntExt} details the interpolation and extrapolation capabilities of each model proposed in this paper.
Conclusions and future work are detailed in Section \ref{sec:Conclusion}.

%----------------------------------------------
\section{Materials and Experiments\label{sec:Materials}}
%----------------------------------------------

%----------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------

The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.

\begin{table}[h!]
\centering
\caption{Chemical composition of AISI P20 steel, Fe = balance.}
\begin{tabular}{lccccccc}
\hline
Element & C & Mn & Mo & Si & Ni & Cr & Cu\\\hline
Wt~\% & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17\\\hline
\label{tab:Composition}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}

Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $R_0$ are the height and radius before compression and $h$, $R_M$ and $R_T$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process.}
\label{fig:GleebleProcess}
\end{figure}

\OP{Here, a part concerning the treatment of the Gleeble data is missing.
You introduce the notions of $h_0$, $R_0$, $h$, $R_M$ and $R_T$ and we have no idea what they are for.
How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}
The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A~\text{and}~\varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
As there are noises from raw data, filter method is applied to remove noise and have more smooth data.
For further usage of  data in numerical simulation elastic parts have been removed.

%------------------------------------------------------------------------
\subsection{Compression tests results\label{sec:ComTestResults}}
%------------------------------------------------------------------------

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}
Almost all data are around $21030$ or less than and the amplitude of deformation is between $0.7$ and $0.85$.
We have decided to limit the identification up to $0.7$ because for strain rates $\mdot\varepsilon=2$ and $\mdot\varepsilon=5$, stresses are note good.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2.0~\ps$, and $5~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{Figures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:RawData}
\end{figure}

>>>>

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}

% This is used to add comments into the text
%
% Will have to be removed from final version
%
\usepackage{soul}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150}
\DeclareRobustCommand{\OP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
\DeclareRobustCommand{\OPP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}

@@

\title{Comparison of Analytical and Artificial Neural Network models in predicting hot deformation behavior of AISI P20}

\author[LGP]{Pierre Tize Mha}
\author[ETS]{Prashant Dhondapure}
\author[LGP]{Amèvi Tongne}
\author[ETS]{Mohammad Jahazi}
\author[LGP]{Olivier Pantalé\corref{cor1}}
\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3, Canada}

\begin{abstract}
An analysis of the use of analytical models and Artificial Neural Networks (ANN) is proposed in this paper to study the high-temperature deformation behavior of AISI P20 alloy during hot compression tests, on a Gleeble thermomechanical simulator, over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
From the experimental data (stress-strain curves), 5 analytical models such as Johnson-Cook (JC), Modified Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arrhenius (AR) and PTM on the one hand, and an ANN model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow stress $\sigma^y$ of this alloy.
The comparison between the analytical models, the ANN model and the experimental results, carried out on the basis of the Mean Absolute Relative Error ($\AARE$) and the Root Mean Square Error ($\RMSE$), allowed us to qualify these models.
We were able to show that the JC and MZA models are not suitable to predict the high temperature behavior of the AISI P20 alloy, while the HS, PTM and AR models can be used to predict the behavior of this alloy with an acceptable error.
On the other hand, the ANN model results show excellent agreement between the predicted flow stresses $\sigma^y$ and experiment with very low error.
To validate the performance of these models, their ability to interpolate and extrapolate the experimental data was also tested.
The HS, PTM and AR analytical models have shown a good interpolation and extrapolation capacity with a notable superiority for the AR model compared to the other two.
The ANN model is still superior to the AR model from the point of view of its global behavior and its performance.
\end{abstract}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------

Continuous casting and rolling techniques are an integral part of material forming methods.
Advantages of this method include increased process efficiency, energy savings, improved casting quality and easier mechanization and automation.
Deformation, a complex process involving simultaneous elastic and plastic deformation, is accompanied by high temperatures, high strain rates, and complex and variable frictional conditions \cite{He-2013}, for which, analytical methods are not available for quantitative study and analysis of the deformation mechanism.
On the other hand, conducting experimental tests is not only time-consuming but also requires a high financial investment \cite{Changizian-2012}.
As an alternative approach to the previous two, the Finite Element Method (FEM) is widely used as a tool for analysis and optimization of process parameters in the processing of various materials.
Finite element modeling effectively compensates for the shortcomings of analytical and experimental methods and is playing an increasingly important role in determining process parameters, improving product quality, and gaining in-depth knowledge of deformation mechanisms.
For example, FEM has been widely used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Mandal-2009, Qin-2010, Ji-2018}.

Hot forming processes are an essential step in the manufacture of mechanical components and directly affect the final quality of the products through their strong influence on the micro-structure and mechanical properties as reported by Ashtiani \eal \cite{Ashtiani-2012}.
Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallization), which very often occur during hot working, influence the behavior and deformation of materials.
The complexity of the thermomechanical behavior usually leads to the fact that it can only be taken into account accurately by using a numerical approach to obtain the response of the material under the specified loading conditions.
To this end, a mathematical formulation is typically used to represent the flow stress $\sigma^y$ of a material from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ in a form that can be used in finite element software \cite{Lin-2008-P, Wu-2012}.

For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models.
Thus, various forms of constitutive equations have been proposed to describe the flow stress of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}.
Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEM codes.
The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{NematNasser-2003, Khan-2004}.
However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior.
We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}.
To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhang-2015, Zhou-2019}.
Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
However, this model has other drawbacks related to the limit value of the test temperature.
Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Lee-2006, Chen-2007}.
Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.

The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the deformation energy of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
Its original formulation has been revised several times to correctly describe the resulting experimental behavior.
In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors.
For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arrhenius model so that his model could predict the high-temperature flow of a magnesium alloy.
Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.

Users of the Forge software make extensive use of the model developed by Hansel and Spittel \cite{Hensel-1978}, commonly referred to as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$.
Unlike the JC model, this formulation is based on parameters that are determined simultaneously.
This model is simple to use and has 8 parameters that are easy to determine.
The limitation of this model is its loss of accuracy in some cases when the 8 parameters are defined.
This is why many works often limit its identification to only 5, 6 or 7 parameters.
This has been verified in our study where the smallest error of the model is obtained with only 7 parameters identified.

@@

Behavior modeling based on an Artificial Neural Network is an approach to predict the flow stress of materials without requiring a mathematical formulation of the flow law.
It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress by an analytical model whose parameters are identified by a classical regression method is limited.
Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
Consequently, ANNs have been successfully applied to predict the flow of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}.
They provide a fundamentally different approach to statistical or numerical techniques for modeling materials.

In this work, the high-temperature thermomechanical behavior of AISI P20 modified carbon steel subjected to compression tests in a Gleeble thermomechanical simulator was studied.
From the experimental data obtained from the compression tests, five analytical models were identified in order to select the one that best describes the behavior of this alloy.
A flow model based on an ANN was also developed and identified, and a comparative study between the 5 analytical models and the ANN model is proposed.
A fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.

The main parts of this work are as follows: Section \ref{sec:Materials} presents the hardware (Gleeble thermomechanical simulator), the experimental procedure, the material and the results of the compression tests performed for this study.
Section \ref{sec:ConstLaws} is devoted to the presentation of the 5 analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models with regard to the experimental results.
Section \ref{sec:IntExt} details the interpolation and extrapolation capabilities of each model proposed in this paper.
Conclusions and future work are detailed in Section \ref{sec:Conclusion}.

%----------------------------------------------------------------------------------
\section{Materials and Experiments\label{sec:Materials}}
%----------------------------------------------------------------------------------

%----------------------------------------------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------------------------------------------

The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of AISI P20 steel, Fe = balance.}
\begin{tabular}{lccccccc}
	\hline
	Element &  C   &  Mn  &  Mo  &  Si  &  Ni  &  Cr  &  Cu  \\ \hline
	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
	\label{tab:Composition}
\end{tabular}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process.}
\label{fig:GleebleProcess}
\end{figure}

The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as true stress and true strain according to L-gauge where the formula to get those curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$ and $F$ is the force as measured by Gleeble load cell.\OPP{those formulas seems incomplete.}
As there are noises from raw data, filter method is applied to remove noise and have more smooth data.\OPP{what is the filtering method used ?}
For further usage of data in numerical simulation elastic parts have been removed. \OPP{you must explain how.}

%----------------------------------------------------------------------------------
\subsection{Compression tests results\label{sec:ComTestResults}}
%----------------------------------------------------------------------------------

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/rawData}
\caption{Stress-strain curves of AISI P20 alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
\label{fig:RawData}
\end{figure}
All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
So, as we have 6 strain rates and 5 temperatures, the database consists of $21~000$ data points.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRV) and Dynamic Recrystallization (DRX).
At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRV.
This DRV mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains.
These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
As an example, Figure \ref{fig:Micrography} shows the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/BeforeCompM}
\caption{Before hot compression}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/AfterCompM}
\caption{After hot compression}
\end{subfigure}
\caption{Optical micrographs of the AISI P20 steel before (a) and after (b) hot compression.}
\label{fig:Micrography}
\end{figure}
As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the 6 proposed flow laws will be presented in the next section in order to predict the behavior of the material in any test condition.

%----------------------------------------------------------------------------------
\section{Identification of constitutive flow laws parameters\label{sec:ConstLaws}}
%----------------------------------------------------------------------------------
